QPLIB: A Library of Quadratic Programming Instances

### 2016-07-28 QPLIB-2.3.tex
included Nick's comments

Local search methods typically require as an input a solution $x'$ and attempt to improve it---either towards feasibility, or towards optimality, or both---using only information that is available in a neighborhood of $x'$. In general, local search methods are incomplete. As remarked above, however, local search methods deployed on a convex problem behave like complete methods, possibly via devices that that allow one to find a feasible starting solution if there is one (the so-called ``phase 0'').

Most local search methods for *C* are iterative in nature, and need a feasible starting point $x^0$ as input. The ($k+1$)-st iterate is obtained as $x^{k+1} = x^k + \alpha_k d^k$, where $\alpha_k$ (a scalar) is the {\it step length}, and $d^k$ (a vector) is the {\it search direction}, e.g.~belonging to a tangent manifold and having a negative directional derivative at $x^k$, in order to improving optimality while reducing infeasibility. Local search methods for *I* are also iterative, but since defining a useful notion of descent direction is harder in presence of integer variables, $d^k$ and $\alpha_k$ are usually computed in different ways, depending on the application at hand.

@@

\paragraph{Active set methods.}
%
At each iteration $k$ the algorithm forms the {\it active set} $\mathcal{A}^k$ containing the (indices of the) {\it active constraints}, i.e., all of the equality constraints as well as the inequality constraints that are satisfied at equality at the current iterate $x^k$. A subproblem, consisting of a minimization of a certain auxiliary objective function subject to all active constraints, is then solved to identify a good search direction $d^k$. An appropriate step length $\alpha_k$ is then found by checking for the inactive constraints (since these must be satisfied too). If at $x^{k+1}$ some of the previously inactive constraints have become active, or vice versa, $\mathcal{A}^k$ is updated accordingly. This general scheme works because the subproblem is defined in such a way as to be (a) easier to solve than the original problem, and (b) helping the sequence $x^k$ to converge to a Karush-Kuhn-Tucker (KKT) point.

>>>>

Local search methods typically require as an input a solution $x'$ and attempt to improve it---either towards feasibility, or towards optimality, or both---using only information that is available in a neighborhood of $x'$. In general, local search methods are incomplete. As remarked above, however, local search methods deployed on a convex problem behave like complete methods, possibly via devices that that allow one to find a feasible starting solution if there is one (like what was used to be called ``phase -1'' in the simplex method).

Most local search methods for *C* are iterative in nature, and need a feasible starting point $x^0$ as input. The ($k+1$)-st iterate is obtained as $x^{k+1} = x^k + \alpha_k d^k$, where $\alpha_k$ (a scalar) is the {\it step length}, and $d^k$ (a vector) is the {\it search direction}, e.g.~belonging to a tangent manifold and having a negative directional derivative at $x^k$, in order to improving optimality while reducing infeasibility. Alternatively, $x^{k+1} = x^k + d^k(\alpha_k)$ where $d^k(\cdot)$ is an arc satisfying $d^k(0) = 0$. Local search methods for *I* are also iterative, but since defining a useful notion of descent direction is harder in presence of integer variables, $d^k$ and $\alpha_k$ are usually computed in different ways, depending on the application at hand.

@@

\paragraph{Active set methods.}
%
At each iteration $k$ the algorithm forms the {\it active set} $\mathcal{A}^k$ containing the (indices of the) {\it active constraints}, i.e., all of the equality constraints as well as the inequality constraints that are satisfied at equality at the current iterate $x^k$. A subproblem, consisting of a minimization of a certain auxiliary objective function and including only active constraints, is then solved to identify a good search direction $d^k$. An appropriate step length $\alpha_k$ is then found by checking for the inactive constraints (since these must be satisfied too). If at $x^{k+1}$ some of the previously inactive constraints have become active, or vice versa, $\mathcal{A}^k$ is updated accordingly. This general scheme works because the step is chosen so that the objective decreases, and the active set cannot repeat.
